Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2018-12-23 paper/ms.tex
Swearing is bad
Update paper

\shortauthors{Beane et al.}
\shorttitle{Where the Hell Are We?}

@@

\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\z}{z}
\newcommand{\uth}{\textsuperscript{th}}

@@

First, a dark matter only simulation was run with $\Lambda$CDM cosmology
parameterized by $\Omega_m = 0.272$, $\Omega_{\Lambda} = 0.728$, $\Omega_b =
0.0455$, $h = 0.702$, $\sigma_8 = 0.807$, and $n_s = 0.961$, consistent with
current constraints \citep{2018arXiv180706209P}. Halos are selected at $z=0$
based solely on their mass ($\sim 1\text{--}2 \times 10^{12} \Msun$).
Particles within $5 R_{200\text{m}}$ of each halo are traced back to $\z=99$
and the initial conditions are regenerated at higher resolution using MUSIC
\citep{2011MNRAS.415.2101H}.

@@

@@

One could then make a further selection by requiring that the action of each
field star $i$ be close to the cluster's actions to within some bound, i.e.
$\bm{J}_i - \bm{J}_c \in V_e$ where $V_e$ is some volume in action space
enclosing a region of acceptable error. A natural choice for $V_e$ is to
center it at the origin and allow its extent to be the intrinsic action-space
dispersion of a disrupted cluster. This dispersion can be estimated as
\citep[\S~8.3.3][]{2008gady.book.....B}
\beq \label{eq:action_disp}
\frac{\Delta J_i}{J_i} \sim \left(\frac{m}{M}\right)^{1/3}\text{,}
\eeq
where $m$ is the mass of the cluster and $M$ is the mass enclosed by the
cluster's orbit. A more sophisticated treatment of the action-space dispersion
of disrupted clusters can be obtained by following
\citet{2011MNRAS.413.1852E}, but such a treatment is premature for this work.

@@

In Figure~\ref{fig:cluster_offset}, we show the $z$ offset necessary to induce
the action space dispersion computed from Equation~\ref{eq:action_disp}, using
the \texttt{gala} computed mass enclosed within a radius of $8.2\,\kpc$ ($\sim
10^{11}\,[\,M_{\odot}\,]$).

From the simulation we have the best handle on the $z$ offset
(Figure~\ref{fig:midplane}), and this $z$ offset has the greatest impact on
the vertical action $J_z$ (Figure~\ref{fig:many_orbit_wrong_ref}). Therefore,
we only consider the impact of a $z$ offset on the vertical action $J_z$.

>>>>

\shortauthors{Beane et al.}
\shorttitle{Our Galactic Midplane}

@@

\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\z}{z_r}
\newcommand{\uth}{\textsuperscript{th}}
\newcommand{\n}{\text{n}}

@@

First, a dark matter only simulation was run with $\Lambda$CDM cosmology
parameterized by $\Omega_m = 0.272$, $\Omega_{\Lambda} = 0.728$, $\Omega_b =
0.0455$, $h = 0.702$, $\sigma_8 = 0.807$, and $n_s = 0.961$, consistent with
current constraints \citep{2018arXiv180706209P}. Halos are selected at $\z=0$
based solely on their mass ($\sim 1\text{--}2 \times 10^{12} \Msun$). In this
work, to avoid confusion with the vertical height $z$, we refer to
cosmological redshift as $\z$. Particles within $5 R_{200\text{m}}$ of each
halo are traced back to $\z=99$ and the initial conditions are regenerated at
higher resolution using MUSIC \citep{2011MNRAS.415.2101H}.

@@

To gain further handle on the midplane behavior as a function of azimuth, we
compute the range of midplane values for a given $\Delta \phi$ segment of the
midplane in Figure~\ref{fig:range_deltaphi}. With the observer's azimuth set
to zero, we consider a region extending from $-\Delta \phi/2$ to
$\Delta\phi/2$. We also compute the chord length for the chord extending from
the observer to $\pm \Delta\phi/2$. We repeat this for each of the $50$ bins
in azimuth. Each bin is plotted as a gray line, with the mean value in solid
blue and the $1\,\sigma$ dispersion as the dashed blue lines.

\begin{figure*}
\plotone{fig/range_dphi.pdf}
\caption{Caption.}
\label{fig:rand_deltaphi}
\end{figure*}

@@

One could then make a further selection by requiring that the action of each
field star $i$ be close to the cluster's actions to within some bound, i.e.
$\bm{J}_i - \bm{J}_c \in V_e$ where $V_e$ is some volume in action space
enclosing a region of acceptable error. A natural choice for $V_e$ is to
center it at the origin and allow its extent to be the intrinsic action-space
dispersion of a disrupted cluster. This dispersion can be estimated as
\citep[\S~8.3.3][]{2008gady.book.....B}
\beq \label{eq:action_disp}
\frac{\Delta J_i}{J_i} \sim \left(\frac{m_c}{M}\right)^{1/3}\text{,}
\eeq
where $m_c$ is the mass of the cluster and $M$ is the mass enclosed by the
cluster's orbit. A more sophisticated treatment of the action-space dispersion
of disrupted clusters can be obtained by following
\citet{2011MNRAS.413.1852E}, but such a treatment is premature for this work.

@@

In Figure~\ref{fig:cluster_offset}, we show the $z$ offset necessary to induce
the action space dispersion computed from Equation~\ref{eq:action_disp}, using
the \texttt{gala} computed mass enclosed within a radius of $8.2\,\kpc$ ($\sim
10^{11}\,M_{\odot}$).

We now convert the $z$~offset-$m_c$ relation to an $R_{\n}$-$m_c$ relation,
where $R_{\n}$ indicates a sort of ``solar neighborhood'' radius. An observer
attempting to reconstruct an open cluster of mass $m_c$ with perfect knowledge
of the midplane at the location of the cluster would expect to find the
ejected members using a dynamical cut for field stars within a distance
$R_{\n}$ of the cluster. If such an observer wants to find ejected stars that
are at a distance greater than $R_{\n}$, a more sophisticated analysis would
be required, the details of which are not apparent to the authors of this
work.

We use the relation in Figure~\ref{fig:deltaphi}, which shows the typical $z$
offset at each $\Delta \phi$, to convert a given $z$ offset into a $\Delta
\phi$, which we then convert into a chord length which we interpret as
$R_{\n}$.
